---
title: "Homework 5"
author: "Annika Godines"
date: "2024-02-29"
output: 
  html_document:
    toc: yes
    toc_float: yes
---
```{r global_options, echo=FALSE, warning = FALSE}
# Set Parameter
knitr::opts_chunk$set(fig.height=5, fig.width=7, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=80))
```

```{r echo = FALSE, warning = FALSE, include = FALSE}
library(ggplot2)
library(knitr)

```

# **Problem 1** : Iron Bank

#### Are the observed data ( 70 flagged trades out of 2021) consistent with the SEC's null hypothesis that, over the long run, securities trades from the Iron Bank are flagged at the same 2.4% baseline rate as that of other traders?

Use Monte Carlo simulation (with at least 100,000 simulations) to calculate a p-value under this null hypothesis

```{r echo = FALSE}
n_simulations <- 100000
# Stimulate using the Null Hypothesis
simulated_flag <- rbinom(100000, 2021, 0.024)
# Calculate 
flag_outcome <- 70
testing <- sum(simulated_flag >= flag_outcome)
# Calculate P
calc_P <- testing / n_simulations


# Plot Graph
hist(simulated_flag, breaks = 50, col = "purple", border = "white", 
     xlab = "Number of Flagged Trades", 
     ylab = "Frequency", 
     main = "Distribution among flagged trades under the null hypothesis:")
abline(v = flag_outcome, col = "red", lwd = 2)
legend("topright", legend = c("Observed Flags", "Simulated Distribution"), 
       col = c("red", "purple"), lwd  = 2)

#####

# Conclusion
if (calc_P < 0.05) {
  conclusion <- "Reject the null hypothesis."
} else {
  conclusion <- "Fail to reject the null hypothesis."
}

# Print p-value and conclusion
cat("p-value:", round(calc_P, 4), "\n")
print(conclusion)
```


# **Problem 2** : Health Inspection

#### Are the observed data for Gourmet Bites consistent with the Health Department's null hypothesis that, on average, restaurants in the city are cited for health code violations at the same 3% baseline rate?

Use a Monte Carlo simulation (with at least 100,000 simulations) to calculate a p-value uncer this null hypothesis. Follow the same answer format as the prior problem.

```{r echo = FALSE}
# Set the parameters
total_inspections <- 1500
total_gourmet_bites_inspections <- 50
total_violations <- 8
baseline_violation_rate <- 0.03
simulations <- 100000

# Function to simulate a single inspection outcome
simulate_inspection <- function() {
  sample_violations <- rbinom(total_inspections, size = 1, prob = baseline_violation_rate)
  sum(sample_violations)
}

# Simulate multiple inspections
simulated_violations <- replicate(simulations, simulate_inspection())

# Calculate p-value
p_value <- mean(simulated_violations >= total_violations)

# Output result
p_value

# Plot histogram of simulated violations
ggplot(data = data.frame(simulated_violations = simulated_violations), aes(x = simulated_violations)) +
  geom_histogram(binwidth = 1, fill = "purple", color = "white") +
  geom_vline(xintercept = total_violations, color = "red") +
  labs(title = "Distribution of Simulated Violations",
       x = "Number of Violations",
       y = "Frequency") +
  theme_minimal()

# Conclusion
if (p_value < 0.05) {
  conclusion <- "Reject the null hypothesis."
} else {
  conclusion <- "Fail to reject the null hypothesis."
}

# Print p-value and conclusion
cat("p-value:", round(p_value, 4), "\n")
print(conclusion)


```


# **Problem 3**: LLM Watermarking
## **Part A** : The Null or Reference Distribution

```{r echo = FALSE, include = FALSE}
# Step 1: 
sentences <- readLines("brown_sentences.txt")

#Step 2:
letter_freq <- read.csv("letter_frequencies.csv")

#Step 3:
calculate_chi_squared <- function(sentence, frequencies) {
  frequencies$Probability <- frequencies$Probability / sum(frequencies$Probability)
  
  # Clean data by removing special characters & convert to uppercase
  clean_sentence <- gsub("[^A-Za-z]", "", sentence)
  clean_sentence <- toupper(clean_sentence)
  
  # Count observed occurrences of each letter
  observed_counts <- table(factor(strsplit(clean_sentence, "")[[1]], levels = frequencies$Letter))
  
  # Calculate expected count
  total_letters <- sum(observed_counts)
  expected_counts <- total_letters * frequencies$Probability
  
  # Calculate chi-squared statistic
  chi_squared_stat <- sum((observed_counts - expected_counts)^2 / expected_counts)
  
  return(chi_squared_stat)
}

# Calculate chi-squared statistic for each sentence in the reference data
chi_squared_values <- sapply(sentences, calculate_chi_squared, frequencies = letter_freq)

#Step 6: 
# print(chi_squared_values)

# Step 5: Summarize the chi-squared statistics
summary(chi_squared_values)

```

```{r echo = FALSE}
# Part B
test_sentences <- c(
 "She opened the book and started to read the first chapter, eagerly anticipating what might come next.",
  "Despite the heavy rain, they decided to go for a long walk in the park, crossing the main avenue by the fountain in the center.",
  "The museum’s new exhibit features ancient artifacts from various civilizations around the world.",
  "He carefully examined the document, looking for any clues that might help solve the mystery.",
  "The students gathered in the auditorium to listen to the guest speaker’s inspiring lecture.",
  "Feeling vexed after an arduous and zany day at work, she hoped for a peaceful and quiet evening at home, cozying up after a quick dinner with some TV, or maybe a book on her upcoming visit to Auckland.",
  "The chef demonstrated how to prepare a delicious meal using only locally sourced ingredients, focusing mainly on some excellent dinner recipes from Spain.",
  "They watched the sunset from the hilltop, marveling at the beautiful array of colors in the sky.",
  "The committee reviewed the proposal and provided many points of useful feedback to improve the project’s effectiveness.",
  "Despite the challenges faced during the project, the team worked tirelessly to ensure its successful completion, resulting in a product that exceeded everyone’s expectations."
)

# Calculate chi-squared statistic for each test sentence
test_chi <- sapply(test_sentences, calculate_chi_squared, frequencies = letter_freq)

# Calculate p-values for each test sentence based on the null distribution
calculate_p <- function(test, null_distribution) {
  number_value_greater_equal <- sum(null_distribution >= test)
  total <- length(null_distribution)
  p_value <- number_value_greater_equal / total
  return(p_value)
}

# Calculate p-values for each test sentence
p_values <- sapply(test_chi, calculate_p, null_distribution = chi_squared_values)

# Show a table of p-values rounded to three decimal places
p_values_table <- data.frame(Sentence = test_sentences, P_Value = round(p_values, 3))


# Create a table of test sentences and their p-values
p_values_table <- data.frame(Sentence = test_sentences, P_Value = round(p_values, 3))

# Print the table using kable
kable(p_values_table, caption = "Table of Test Sentences and their P-Values", align = "c", row.names = FALSE)

```

## **Part B**: Checking for a Watermark

```{r echo = FALSE}
# Identify the sentence with the lowest p-value
watermarked_sentence <- test_sentences[which.min(p_values)]
cat("The sentence likely produced by an LLM with a watermark:\n", watermarked_sentence, "\n")
```

